Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
adds abstract

\title{Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title

@@

\begin{abstract}
The abstract should summarize the contents of the paper. LNCS guidelines
indicate it should be at least 70 and at most 150 words. It should be set in 9-point
font size and should be inset 1.0~cm from the right and left margins.
\dots
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

@@

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.35\textwidth}
			\includegraphics[width=4.2cm]{fig/graffig.jpg}
		\end{minipage}
		\begin{minipage}{.2\textwidth}
			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
	\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
	\end{minipage}\vspace{-0cm}\\
\begin{minipage}{.35\textwidth}
	---
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny
	{\textsl{dalmatian, dog, heeler}}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\textsl{\tiny dog}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny \textsl{dog}
\end{minipage}
	\end{center}
	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
	\label{fig:graf_genome}
\end{figure}

@@

\subsection{ImageNet}

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories. ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.

@@

\subsection{\refcoco and \refcocop \cite{Yu2016}}
Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco}, 
%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
%However, the COCO region-level (object) annotations are not linked to the captions.
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player game, which was designed to obtain REs uniquely referring to the target objects in an image. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
If the matcher's prediction is correct, the RE is considered valid.

@@

\subsection{Object detectors}
As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.

\subsection{Post-annotating COCO Captions}
Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation. 
%
In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
such that natural language phrases first needed to be aligned with the image regions they refer to. 
This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study. 
% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)

>>>>

\title{Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title

@@

\begin{abstract}
Massive data collections that are of interest for language \& vision tasks (from image captioning to visual dialogue) are nowadays available. In principle, these could constitute valuable resources also for research in Linguistics, besides application-oriented one. However, in practice very few studies have tested linguistic hypotheses using these large-scale datasets. In this paper, we illustrate the challenges of using this type of corpora for linguistic research, by focusing on a case study, namely the context-dependence of object naming in real-world images. Our analysis of existing resources in language \& vision reveals that none of the available datasets consistently satisfies all of the requirements for a linguistically motivated study of this phenomenon. We conclude with a proposal for a more consistent annotation of language \& vision data which can aid the study of object naming.
%The abstract should summarize the contents of the paper. LNCS guidelinesindicate it should be at least 70 and at most 150 words. It should be set in 9-point font size and should be inset 1.0~cm from the right and left margins.
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

@@

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.52\textwidth}
			\includegraphics[width=\linewidth]{fig/graffig.pdf}
		\end{minipage}
		\begin{minipage}{.42\textwidth}
			\includegraphics[width=5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\end{center}
	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
	\label{fig:graf_genome}
\end{figure}

@@

\subsection{ImageNet and ILSVRC}

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories. ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) without any (or very few) distractors objects in context.

@@

\subsection{\refcoco and \refcocop \cite{Yu2016}}~\\ 
Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco}, 
%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
%However, the COCO region-level (object) annotations are not linked to the captions.
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player game, which was designed to obtain REs uniquely referring to the target objects in an image. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
If the matcher's prediction is correct, the RE is considered valid.

@@

\subsection{Post-annotating CoCo Captions}
Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation. 
%
In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
such that natural language phrases first needed to be aligned with the image regions they refer to. 
This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study. 
% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
